visitation_bias

### 2021-03-03 code/bias_niche.Rmd
oops

# 1. Abundance of floral morphotypes through elevation and time

## 1.1 Get absolute and percent flower cover by morphotype
```{r}
ktype_abund <- flower_cover %>%
  left_join(fl_traits) %>%
  group_by(site, date, k.type.ss) %>%
  summarize(flower.cover = sum(flower.cover)) %>%
  left_join(site_data) %>%
  mutate(ktype = factor(k.type.ss),
         year = factor(year(date)),
         yday = yday(date),
         site = factor(site)) %>%
  group_by(site, date) %>%
  mutate(prop.flower.cover = flower.cover/sum(flower.cover))
```

## 1.2 Fit elevation*time tensor-product GAMs 
```{r}
# Prop abundance; this works well with a quasibinomial distribution
gam_ktype_propabund <- bam(prop.flower.cover ~
                             s(ktype, bs = "re") +
                             te(yday, elev.mean, by = ktype, bs = c("gp", "tp"), k = 8),
                           family = "quasibinomial",
                           method = "fREML",
                           discrete = TRUE,
                           select  = TRUE,
                           data = filter(ktype_abund, !ktype %in% c("9", "10"))) %>% getViz()

check.gamViz(gam_ktype_propabund)
summary(gam_ktype_propabund)

# Absolute abundance; I find that I really have to log-transform absolute flower cover to fit a good model
gam_ktype_abund <- bam(log(flower.cover) ~
                         s(ktype, bs = "re") +
                         te(yday, elev.mean, by = ktype, bs = c("gp", "tp"), k = 8),
                       family = "scat", # to account for heavy tails
                       method = "fREML",
                       discrete = TRUE,
                       select  = TRUE,
                       data = filter(ktype_abund, !ktype %in% c("9", "10"))) %>% getViz()

check.gamViz(gam_ktype_abund)
summary(gam_ktype_abund)
```

## 1.3 Plot morphotype abundances
```{r}
k1_abund <- plot(sm(gam_ktype_abund, 2))
k2_abund <- plot(sm(gam_ktype_abund, 3))
k3_abund <- plot(sm(gam_ktype_abund, 4))
k4_abund <- plot(sm(gam_ktype_abund, 5))
k5_abund <- plot(sm(gam_ktype_abund, 6))
k6_abund <- plot(sm(gam_ktype_abund, 7))
k7_abund <- plot(sm(gam_ktype_abund, 8))

k1_propabund <- plot(sm(gam_ktype_propabund, 2))
k2_propabund <- plot(sm(gam_ktype_propabund, 3))
k3_propabund <- plot(sm(gam_ktype_propabund, 4))
k4_propabund <- plot(sm(gam_ktype_propabund, 5))
k5_propabund <- plot(sm(gam_ktype_propabund, 6))
k6_propabund <- plot(sm(gam_ktype_propabund, 7))
k7_propabund <- plot(sm(gam_ktype_propabund, 8))

ktype_abund_grid <- gridPrint(

                       k1_propabund + l_fitRaster() + l_fitContour() + 
                         labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       k2_propabund + l_fitRaster() + l_fitContour() + 
                         labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       k3_propabund + l_fitRaster() + l_fitContour() + 
                         labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       k4_propabund + l_fitRaster() + l_fitContour() + 
                         labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       k5_propabund + l_fitRaster() + l_fitContour() + 
                         labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE), 
                       k6_propabund + l_fitRaster() + l_fitContour() + 
                         labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       k7_propabund + l_fitRaster() + l_fitContour() + 
                         labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),

                       k1_abund + l_fitRaster() + l_fitContour() + 
                         labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       k2_abund + l_fitRaster() + l_fitContour() + 
                         labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       k3_abund + l_fitRaster() + l_fitContour() + 
                         labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       k4_abund + l_fitRaster() + l_fitContour() + 
                         labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       k5_abund + l_fitRaster() + l_fitContour() + 
                         labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE), 
                       k6_abund + l_fitRaster() + l_fitContour() + 
                         labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       k7_abund + l_fitRaster() + l_fitContour() + 
                         labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),

                       ncol = 7)

ggsave(ktype_abund_grid, file = "../output/ktype_abund_gam.pdf", height = 3, width = 12)
```

# 1. Overall bias ** Need to refit these models without ktype 0 since it seems that these plants were ignored during floral surveying (always assigned cover = 0), and therefore I have no abundance data with which to compare visitation **

@@

# 2 Ordination of dietary niche
Aggregation changes meaning. Don't forget that. When I pool visitation across dates, I am introducing the effects of relative abundance and floral phenology. Species in bloom when BB abundance is high will be over-represented, and vice-versa. And species with a long bloom time will be over-represented, and vice-versa. This isn't necessarily a problem. I just need to make sure I interpret the results the right way. When I pool data like this, I am comparing the "net" diet of species, which includes the effects of abundance and phenology in addition to the effects of floral preferences. I think that is appropriate for this stage of the analysis, but I need to be careful not to assume that what I'm doing here is the same sort of analysis as what I did above without pooling samples. 
```{r}
# Fl traits with abbreviated names
fl_traits2 <- fl_traits %>%
  left_join(read_csv("../data/processed_data/network.csv")) %>%
  select(plant.sp, plant.sp.abb, plant.genus, plant.family, k.type.ss, color) %>%
  mutate(k.type.ss = factor(k.type.ss)) %>%
  distinct()

@@

# 4. The lability of bias
## 4.1 How does the foraging bias of each species with respect to each morphotype vary through elevation and time?
```{r}
# Subset data to include only abundant BB spp 
gam_data <- prop_visits_ktype %>%
  filter(!ktype %in% c("0", "9", "10") & # focus on major ktypes
           bb.sp %in% c("telu", "prat", "pasc", "hort", "soro", "wurf")) %>% # focus on abundance bb.sp
  unite(pair, c(bb.sp, ktype), sep = "_", remove = FALSE) %>% # paste bb.sp and ktype into pair
  mutate(pair = factor(pair),
         bin.visits = if_else(visits > 0, 1, 0), # binarize visitation
         year = factor(year(date)),
         site = factor(site))

# Independent smooth model
gam_pvis_elev01 <- bam(bin.visits ~
                         s(pair, bs = "re") + # center by pair
                         bb.sp.abund:perc.flower.cover + # condition on a global bb/fl abundance term
                         perc.flower.cover:pair + # condition on a pair-specific fl abundance
                         te(yday, elev.mean, by = pair, bs = c("gp", "tp"), k = 5), # conditional effects of yday/elev by pair
                       family = "binomial", # binomial response
                       method = "fREML",
                       discrete = TRUE,
                       select =  TRUE,
                       data = filter(gam_data,
                                     bb.sp %in% c("soro", "wurf", "hort",
                                                  "telu", "pasc", "prat"))) %>%
  getViz()

gam_pvis_elev01.sum <- summary(gam_pvis_elev01)
check.gamViz(gam_pvis_elev01)
concurvity(gam_pvis_elev01)
```

### 4.1.1 Plot 
```{r}
hort1 <- plot(sm(gam_pvis_elev01, 2))
hort2 <- plot(sm(gam_pvis_elev01, 3))
hort3 <- plot(sm(gam_pvis_elev01, 4))
hort4 <- plot(sm(gam_pvis_elev01, 5))
hort5 <- plot(sm(gam_pvis_elev01, 6))
hort6 <- plot(sm(gam_pvis_elev01, 7))
hort7 <- plot(sm(gam_pvis_elev01, 8))

pasc1 <- plot(sm(gam_pvis_elev01, 9))
pasc2 <- plot(sm(gam_pvis_elev01, 10))
pasc3 <- plot(sm(gam_pvis_elev01, 11))
pasc4 <- plot(sm(gam_pvis_elev01, 12))
pasc5 <- plot(sm(gam_pvis_elev01, 13))
pasc6 <- plot(sm(gam_pvis_elev01, 14))
pasc7 <- plot(sm(gam_pvis_elev01, 15))

prat1 <- plot(sm(gam_pvis_elev01, 16))
prat2 <- plot(sm(gam_pvis_elev01, 17))
prat3 <- plot(sm(gam_pvis_elev01, 18))
prat4 <- plot(sm(gam_pvis_elev01, 19))
prat5 <- plot(sm(gam_pvis_elev01, 20))
prat6 <- plot(sm(gam_pvis_elev01, 21))
prat7 <- plot(sm(gam_pvis_elev01, 22))

soro1 <- plot(sm(gam_pvis_elev01, 23))
soro2 <- plot(sm(gam_pvis_elev01, 24))
soro3 <- plot(sm(gam_pvis_elev01, 25))
soro4 <- plot(sm(gam_pvis_elev01, 26))
soro5 <- plot(sm(gam_pvis_elev01, 27))
soro6 <- plot(sm(gam_pvis_elev01, 28))
soro7 <- plot(sm(gam_pvis_elev01, 29))

telu1 <- plot(sm(gam_pvis_elev01, 30))
telu2 <- plot(sm(gam_pvis_elev01, 31))
telu3 <- plot(sm(gam_pvis_elev01, 32))
telu4 <- plot(sm(gam_pvis_elev01, 33))
telu5 <- plot(sm(gam_pvis_elev01, 34))
telu6 <- plot(sm(gam_pvis_elev01, 35))
telu7 <- plot(sm(gam_pvis_elev01, 36))

wurf1 <- plot(sm(gam_pvis_elev01, 37))
wurf2 <- plot(sm(gam_pvis_elev01, 38))
wurf3 <- plot(sm(gam_pvis_elev01, 39))
wurf4 <- plot(sm(gam_pvis_elev01, 40))
wurf5 <- plot(sm(gam_pvis_elev01, 41))
wurf6 <- plot(sm(gam_pvis_elev01, 42))
wurf7 <- plot(sm(gam_pvis_elev01, 43))

pterm1 <- plot(pterm(gam_pvis_elev01, 1))
pterm2 <- plot(pterm(gam_pvis_elev01, 2))

grid_plot <- gridPrint(hort1 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       hort2 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       hort3 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       hort4 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       hort5 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE), 
                       hort6 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       hort7 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       pasc1 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       pasc2 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       pasc3 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       pasc4 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       pasc5 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE), 
                       pasc6 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       pasc7 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       prat1 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       prat2 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       prat3 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       prat4 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       prat5 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE), 
                       prat6 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       prat7 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       soro1 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       soro2 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       soro3 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       soro4 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       soro5 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE), 
                       soro6 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       soro7 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       telu1 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       telu2 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       telu3 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       telu4 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       telu5 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE), 
                       telu6 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       telu7 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       wurf1 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       wurf2 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       wurf3 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       wurf4 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       wurf5 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE), 
                       wurf6 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       wurf7 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                       ncol = 7)

ggsave(grid_plot, file = "../output/ktype_lability_gam.pdf", height = 9, width = 12)
```

### Another way to ask this question is to see how the visitation probability changes if I drop the floral abundance term
```{r}
gam_pvis_elev01_unconditioned <- bam(bin.visits ~
                         s(pair, bs = "re") + # center by pair
                         s(year, bs = "re") +
                         bb.sp.abund +
                         te(yday, elev.mean, by = pair, bs = c("gp", "tp"), k = 5), # conditional effects of yday/elev by pair
                       family = "binomial", # binomial response
                       method = "fREML",
                       discrete = TRUE,
                       select =  TRUE,
                       data = filter(gam_data,
                                     bb.sp %in% c("soro", "wurf", "hort",
                                                  "telu", "pasc", "prat"))) %>%
  getViz()

check.gamViz(gam_pvis_elev01_unconditioned)

print(plot(gam_pvis_elev01_unconditioned, allTerms = TRUE), pages = 1)

u_hort3 <- plot(sm(gam_pvis_elev01_unconditioned, 3))
u_hort5 <- plot(sm(gam_pvis_elev01_unconditioned, 4))
u_hort6 <- plot(sm(gam_pvis_elev01_unconditioned, 5))
u_hort7 <- plot(sm(gam_pvis_elev01_unconditioned, 6))

u_pasc3 <- plot(sm(gam_pvis_elev01_unconditioned, 7))
u_pasc5 <- plot(sm(gam_pvis_elev01_unconditioned, 8))
u_pasc6 <- plot(sm(gam_pvis_elev01_unconditioned, 9))
u_pasc7 <- plot(sm(gam_pvis_elev01_unconditioned, 10))

u_prat3 <- plot(sm(gam_pvis_elev01_unconditioned, 11))
u_prat5 <- plot(sm(gam_pvis_elev01_unconditioned, 12))
u_prat6 <- plot(sm(gam_pvis_elev01_unconditioned, 13))
u_prat7 <- plot(sm(gam_pvis_elev01_unconditioned, 14))

u_soro3 <- plot(sm(gam_pvis_elev01_unconditioned, 15))
u_soro5 <- plot(sm(gam_pvis_elev01_unconditioned, 16))
u_soro6 <- plot(sm(gam_pvis_elev01_unconditioned, 17))
u_soro7 <- plot(sm(gam_pvis_elev01_unconditioned, 18))

u_telu3 <- plot(sm(gam_pvis_elev01_unconditioned, 19))
u_telu5 <- plot(sm(gam_pvis_elev01_unconditioned, 20))
u_telu6 <- plot(sm(gam_pvis_elev01_unconditioned, 21))
u_telu7 <- plot(sm(gam_pvis_elev01_unconditioned, 22))

u_wurf3 <- plot(sm(gam_pvis_elev01_unconditioned, 23))
u_wurf5 <- plot(sm(gam_pvis_elev01_unconditioned, 24))
u_wurf6 <- plot(sm(gam_pvis_elev01_unconditioned, 25))
u_wurf7 <- plot(sm(gam_pvis_elev01_unconditioned, 26))

u_hort3
u_pasc3
u_prat3
u_soro3
u_telu3
u_wurf3

u_hort5
u_pasc5
u_prat5
u_soro5
u_telu5
u_wurf5

u_hort6
u_pasc6
u_prat6
u_soro6
u_telu6
u_wurf6

u_hort7
u_pasc7
u_prat7
u_soro7
u_telu7
u_wurf7

grid_plot <- gridPrint(u_hort3 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_hort5 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE), 
                        u_hort6 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_hort7 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_pasc3 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_pasc5 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE), 
                        u_pasc6 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_pasc7 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_prat3 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_prat5 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE), 
                        u_prat6 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_prat7 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_soro3 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_soro5 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE), 
                        u_soro6 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_soro7 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_telu3 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_telu5 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE), 
                        u_telu6 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_telu7 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_wurf3 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_wurf5 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE), 
                        u_wurf6 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        u_wurf7 + l_fitRaster() + l_fitContour() + labs(title = NULL, x = NULL, y = NULL) + guides(fill=FALSE),
                        ncol = 4)
```

# Hmm...so it looks like floral abundance just isn't driving visitation patterns very strongly. Removing it from the model hardly changes anything, but modeling just floral abundance gives very different patterns than modeling visitation. I suppose we can look at this directly
```{r}
ggplot(gam_data, aes(perc.flower))
```

# But it looks like BB abundance is a very strong driver. What if we remove that from the model?
```{r}

# Let's try some alternative formulations 
```{r}
# We could try using all the ktypes but still sticking to just the major BBs
gam_data2 <- prop_visits_ktype %>%
  filter(ktype %in% c("1", "2", "3", "4", "5", "6", "7") & # focus on major ktypes
           bb.sp %in% c("telu", "prat", "pasc", "hort", "soro", "wurf")) %>% # focus on abundance bb.sp
  unite(pair, c(bb.sp, ktype), sep = "_", remove = FALSE) %>% # paste bb.sp and ktype into pair
  mutate(pair = factor(pair),
         bin.visits = if_else(visits > 0, 1, 0)) # binarize visitation

gam_pvis_elev_alt00 <- bam(bin.visits ~
                             s(pair, bs = "re") + # center by pair
                             bb.sp.abund*perc.flower.cover + # condition on a global bb/fl abundance term
                             perc.flower.cover*pair + # condition on a pair-specific fl abundance
                             #s(perc.flower.cover, by = pair, k = 3) +  term
                             te(yday, elev.mean, by = pair, bs = c("gp", "tp"), k = 5), # conditional effects of yday/elev by pair
                           family = "binomial", # binomial response
                           method = "fREML",
                           discrete = TRUE,
                           select =  TRUE,
                           data = filter(gam_data2,
                                         bb.sp %in% c("soro", "wurf", "hort",
                                                      "telu", "pasc", "prat"))) %>% getViz()

check.gamViz(gam_pvis_elev_alt00)
sum_alt00 <- summary(gam_pvis_elev_alt00)
print(plot.gamViz(gam_pvis_elev_alt00, allTerms = TRUE), pages = 1)

# We could also try a count model
gam_pvis_elev_alt01 <- bam(visits ~
                             s(pair, bs = "re") + # center by pair
                             bb.sp.abund*perc.flower.cover + # condition on a global bb/fl abundance term
                             perc.flower.cover*pair + # condition on a pair-specific fl abundance
                             #s(perc.flower.cover, by = pair, k = 3) +  term
                             te(yday, elev.mean, by = pair, bs = c("gp", "tp"), k = 5), # conditional effects of yday/elev by pair
                           family = "quasipoisson", # Poisson response
                           method = "fREML",
                           discrete = TRUE,
                           select =  TRUE,
                           data = filter(gam_data,
                                         bb.sp %in% c("soro", "wurf", "hort",
                                                      "telu", "pasc", "prat"))) %>% getViz()

check.gamViz(gam_pvis_elev_alt01)
sum_alt01 <- summary(gam_pvis_elev_alt01)
print(plot.gamViz(gam_pvis_elev_alt01, allTerms = TRUE), pages = 1)
plot.gamViz(pterm(gam_pvis_elev_alt01, 1))

# Can we say that certain morphotypes are preferred when overall resources are scarce?
```{r}
### Floral survey data
survey <- read_csv("../data/processed_data/floral_survey.csv") %>%
  semi_join(visitation, by = "plant.sp") %>% # Consider only visited plant species (anytime anywhere, not specifically for a given site*date)
  dplyr::select(site, date, plant.sp, flower.cover) %>%
  group_by(plant.sp) %>%
  mutate(present = case_when(
    max(flower.cover) > 0 ~ TRUE,
    max(flower.cover) == 0 ~ FALSE
  )) %>%
  filter(present == TRUE) # Ignore plants that never had any flower cover

fl_abund_sp <- survey %>%
  group_by(site, date, plant.sp) %>% # group by plant.sp*transect
  summarize(fl.abund = sum(flower.cover)) %>% # get plant.sp*transect total flower cover; this step really shouldn't be required, but in a few cases, there is more than one abundance entry for the same species on a given transect; not sure how that happened, but it's in the original data that Fabrice sent me; alternatively, I could drop the dups or average them. We'll see what Kalli and Fabrice have to say.
  group_by(site, date) %>%
  mutate(prop.fl.abund = fl.abund/sum(fl.abund)) %>% # get the proportional flower cover for each species.
  ungroup() %>%
  #full_join(dplyr::select(net, site, date, plant.sp), by = c("site", "date", "plant.sp")) %>% # add the handful of species occurring in the visitation network but missing from the survey data
  complete(site, date, plant.sp, fill = list(fl.abund = 0, prop.fl.abund = 0)) %>%
  semi_join(survey, by = c("site", "date")) %>%  # only include site-dates that actually occurred
  unique() %>%
  mutate(year = factor(year(date))) %>%
  left_join(fl_traits)

weights <- fl_abund_sp %>%
  select(plant.sp, plant.genus) %>%
  unique() %>%
  left_join(select(visitation, bb.sp, plant.sp)) %>%
  select(plant.genus, bb.sp) %>%
  distinct() %>%
  mutate(visited = rep(1, n())) %>%
  pivot_wider(values_from = visited, names_from = bb.sp, values_fill = 0) %>%
  pivot_longer(cols = 2:17, values_to = "visited", names_to = "bb.sp")

weighted_fl_abund <- fl_abund_sp %>%
  group_by(site, date, plant.genus) %>%
  summarize(flower.cover = sum(fl.abund)) %>%
  left_join(weights) %>%
  mutate(weighted.flower.cover = flower.cover*visited) %>%
  group_by(site, date, bb.sp) %>%
  summarize(total.weighted.flower.cover = sum(weighted.flower.cover)) %>%
  left_join(site_data) %>%
  select(site, date, elev.mean, bb.sp, total.weighted.flower.cover) %>%
  mutate(yday = yday(date),
         bb.sp = factor(bb.sp),
         site = factor(site),
         year = factor(year(date))) %>%
  filter(bb.sp %in% c("pasc", "prat", "soro", "wurf", "telu", "hort"))

dat <- gam_data %>%
  left_join(weighted_fl_abund) %>%
  mutate(perc.vis = (visits/bb.sp.abund)*100,
         pref = perc.vis - perc.flower.cover)

ggplot(dat, aes(log(total.weighted.flower.cover), pref, color = ktype)) +
  geom_point(alpha = 0.25) +
  geom_smooth() +
  facet_wrap(~bb.sp)

gam0 <- bam(bin.visits ~
                 s(pair, bs = "re") + # center by pair
                 bb.sp.abund*perc.flower.cover + # condition on a global bb/fl abundance term
                 perc.flower.cover*pair + # condition on a pair-specific fl abundance
                 s(total.weighted.flower.cover, by = ktype),
               family = "binomial", # binomial response
               method = "fREML",
               discrete = TRUE,
               select =  TRUE,
               data = filter(dat,
                             bb.sp %in% c("soro", "wurf", "hort",
                                          "telu", "pasc", "prat"))) %>%
    getViz()

brm_lability00 <- brm(as.integer(visits.bin) ~
                        bb.sp.abund*perc.flower.cover +
                        total.weighted.flower.cover +
                        (1 + perc.flower.cover + total.weighted.flower.cover | ktype:bb.sp) + 
                        (1 | site), # a random intercept and for site
                      family = "bernoulli", 
                      #file = "../output/brm_lability_00",  # for running locally
                      file = "brm_lability_00", # for running on the HPC
                      chains = 4,
                      cores = 12,
                      iter = 2000,
                      data = dat)

library(glmmTMB)
library(sjPlot)

glm_lability00 <- glmmTMB(as.integer(bin.visits) ~
                            perc.flower.cover*bb.sp.abund +
                            total.weighted.flower.cover*pair +
                            (1 + perc.flower.cover | pair) +
                            (1 | site), # a random intercept and for site
                          family = "binomial", 
                          data = dat)

summary(glm_lability00)

plot_model(glm_lability00)

# Is preference labile at the level of individual floral species? We could pick out a widely distributed representative of each morphotype and see
```{r}
flower_distributions2012 <- flower_cover %>%
  mutate(yday = yday(date),
         year = year(date)) %>%
  filter(year == 2012) %>%
  left_join(site_data) %>%
  left_join(fl_traits)

# Choose the top three most frequently observed species of each morphotype
top_sp_in_morph_2012 <- flower_distributions2012 %>%
  filter(!k.type.ss %in% c("0", "9", "10")) %>%
  group_by(plant.sp, k.type.ss) %>%
  summarize(obs = n()) %>%
  group_by(k.type.ss) %>%
  top_n(3, obs) %>%
  arrange(k.type.ss, -obs)

# Disc (1)
ggplot(filter(flower_distributions2012, plant.sp == "Potentilla erecta"), aes(yday, elev.mean)) +
  geom_point(alpha = 0.25, aes(size = flower.cover))

ggplot(filter(flower_distributions2012, plant.sp == "Alchemilla vulgaris"), aes(yday, elev.mean)) +
  geom_point(alpha = 0.25, aes(size = flower.cover))

ggplot(filter(flower_distributions2012, plant.sp == "Ranunculus acris"), aes(yday, elev.mean)) +
  geom_point(alpha = 0.25, aes(size = flower.cover))

# Funnel (2)
ggplot(filter(flower_distributions2012, plant.sp == "Gentiana aspera"), aes(yday, elev.mean)) +
  geom_point(alpha = 0.25, aes(size = flower.cover))

ggplot(filter(flower_distributions2012, plant.sp == "Gentiana clusii"), aes(yday, elev.mean)) +
  geom_point(alpha = 0.25, aes(size = flower.cover))

ggplot(filter(flower_distributions2012, plant.sp == "Valeriana tripteris"), aes(yday, elev.mean)) +
  geom_point(alpha = 0.25, aes(size = flower.cover))

# Bell (3)
ggplot(filter(flower_distributions2012, plant.sp == "Campanula scheuchzeri"), aes(yday, elev.mean)) +
  geom_point(alpha = 0.25, aes(size = flower.cover))

ggplot(filter(flower_distributions2012, plant.sp == "Soldanella alpina"), aes(yday, elev.mean)) +
  geom_point(alpha = 0.25, aes(size = flower.cover))

ggplot(filter(flower_distributions2012, plant.sp == "Geum rivale"), aes(yday, elev.mean)) +
  geom_point(alpha = 0.25, aes(size = flower.cover))

>>>>

# 1. Overall bias

@@

# 2. Ordination of dietary niche
Aggregation changes meaning. Don't forget that. When I pool visitation across dates, I am introducing the effects of relative abundance and floral phenology. Species in bloom when BB abundance is high will be over-represented, and vice-versa. And species with a long bloom time will be over-represented, and vice-versa. This isn't necessarily a problem. I just need to make sure I interpret the results the right way. When I pool data like this, I am comparing the "net" diet of species, which includes the effects of abundance and phenology in addition to the effects of floral preferences. I think that is appropriate for this stage of the analysis, but I need to be careful not to assume that what I'm doing here is the same sort of analysis as what I did above without pooling samples. 
```{r}
# Fl traits with abbreviated names
fl_traits2 <- fl_traits %>%
  left_join(read_csv("../data/processed_data/network.csv")) %>%
  select(plant.sp, plant.sp.abb, plant.genus, plant.family, k.type.ss, color) %>%
  mutate(k.type.ss = factor(k.type.ss)) %>%
  distinct()

@@

# 3. Dietary niche overlap (i.e. potential competition)

## 3.1 Check BB distribution patterns to decide whom to retain in the analysis
```{r}
bb_distribution <- visitation %>%
  mutate(year = year(date)) %>%
  left_join(site_data) %>%
  group_by(site, date, elev.mean, bb.sp, year) %>%
  summarize(abund = n()) %>%
  group_by(site, elev.mean, bb.sp, year) %>%
  summarize(abund = mean(abund)) %>%
  group_by(bb.sp) %>%
  mutate(elev.floor = min(elev.mean),
         elev.ceiling = max(elev.mean),
         elev.range = elev.ceiling - elev.floor,
         elev.med = elev.floor + ((elev.ceiling - elev.floor)/2))

ggplot(bb_distribution, aes(reorder(bb.sp, elev.med), elev.mean)) +
  geom_line(size = 2, alpha = 0.25) +
  geom_point(aes(size = abund), alpha = 0.5) +
  facet_wrap(~year, ncol = 1) +
  theme_light(12) +
  scale_size_continuous(name = "Abundance") +
  xlab("BB species") +
  ylab("Elevation") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## 3.2 Prep data for calculating niche overlap
```{r}
niche_data <- visitation %>%
  #filter(!bb.sp %in% c("humi", "muci", "gers")) %>%
  left_join(fl_traits) %>%
  mutate(year = factor(year(date)))
```

## 3.3 Function for calculating niche overlap
```{r}
niche_overlapper <- function(x, criterion) {
